---
title: "Environmentalist Analysis"
author: "Elizabeth Hiroyasu"
date: "June 27, 2017"
output: html_document
---
This analysis examines the role of framing in invasive species management specifically for environmentalists versus non-environmentalists.

```{r}
require(Rmisc)
library(ggplot2)
kuni_df <- read.csv("kunisurvey_coded_march16.csv", h=T)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
attach(kuni_df)
NEP <- (as.numeric(nep1) + (6-as.numeric(nep2_rev)) + (6-as.numeric(nep3_rev))
        + as.numeric(nep4) + as.numeric(nep5))/5
#summary(NEP) #mean=3.30, median=3.2; 25%=2.6, 75%=3.8
hist(NEP) #pretty close to normally distributed
#sd(na.omit(NEP))
nep2 <- 6-nep2_rev
nep3 <- 6-nep3_rev
NEP_table <- cbind(nep1, nep2, nep3, nep4, nep5)

#Environmentalism
quantile(NEP, na.rm=T) #25%=2.6, 75%=3.8
enviro_df <- subset(kuni_df, NEP>=3.8)
nonenviro_df <- subset(kuni_df, NEP<=2.6)
```

#Environmentalists
```{r, echo=FALSE, warning=FALSE, message=FALSE}
attach(enviro_df)
enviro_df<-df.treat(df=enviro_df, treat=treat_enviros)
support_enviro <- as.numeric(project_support==1)
summary(project_support)
summary(logit_enviro <- glm(support_enviro ~ as.factor(treat_cat), data=enviro_df, family=binomial(link="logit"))) 
envsupp.df<-treat_func(enviro_df)
envsupp.df$type<-as.factor(1)
```


#Non-Environmentalists
```{r, echo=FALSE, warning=FALSE, message=FALSE}
attach(nonenviro_df)
nonenviro_df<-df.function(df=nonenviro_df, treat=treat_nonenviro)
support_nonenviro<-as.numeric(project_support==1)
summary(project_support)
nonenvsupp.df<-treat_func(nonenviro_df)
nonenvsupp.df$type<-as.factor(2)


theme_update(plot.title = element_text(hjust = 0.5))

environmentalism.df<-rbind.data.frame(envsupp.df, nonenvsupp.df)
ggplot(environmentalism.df, aes(x=treat_cat, y=ATE, fill=type)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=ATE-se, ymax=ATE+se),
                width=.2, position=position_dodge(.9)) +
  xlab("Treatment Category") + ylab("Average Treatment Effect")+
  scale_fill_hue(name="Environmentalism", labels=c("Environmentalists", "Non-Environmentalists")) +
  ggtitle("Treatment Effect by Environmental Identification")
```

#FOR POOLED ENVIRO/ECONOMIC
mean(support_enviro[treat_enviro=="econgain" | treat_enviro=="econloss"])
mean(support_enviro[treat_enviro=="control"])
length(support_enviro[treat_enviro=="econgain" | treat_enviro=="econloss"])
.002 + c(-qnorm(0.975),qnorm(0.975))*sqrt((1/146)*.002*(1-.002))
#ATE=-.002, N=214, 95% CI is -.009 - .005

mean(support_nonenviro[treat_nonenviro=="econgain" | treat_reps=="econloss"], na.rm=T)
mean(support_nonenviro[treat_nonenviro=="control"], na.rm=T)
length(support_nonenviro[treat_nonenviro=="econgain" | treat_nonenviro=="econloss"])
.161 + c(-qnorm(0.975),qnorm(0.975))*sqrt((1/108)*.161*(1-.161))
#ATE=.161, N=108, 95% CI is .092 - .230

#FOR ENVIRO/ECOLOGICAL
mean(support_enviro[treat_enviro=="ecogain" | treat_enviro=="ecoloss"])
mean(support_enviro[treat_enviro=="control"])
length(support_enviro[treat_enviro=="ecogain" | treat_enviro=="ecoloss"])
.176 + c(-qnorm(0.975),qnorm(0.975))*sqrt((1/124)*.176*(1-.176))
#ATE=.176, N=124, 95% CI is .109 - .243

mean(support_nonenviro[treat_nonenviro=="ecogain" | treat_reps=="ecoloss"], na.rm=T)
mean(support_nonenviro[treat_nonenviro=="control"], na.rm=T)
length(support_nonenviro[treat_nonenviro=="ecogain" | treat_nonenviro=="ecoloss"])
.230 + c(-qnorm(0.975),qnorm(0.975))*sqrt((1/131)*.230*(1-.230))
#ATE=.230, N=108, 95% CI is .158 - .302


mean(support_inds[treat_inds=="econgain" | treat_inds=="econloss"])
mean(support_inds[treat_inds=="control"])
length(support_inds[treat_inds=="econgain" | treat_inds=="econloss"])
.113 + c(-qnorm(0.975),qnorm(0.975))*sqrt((1/85)*(.113)*(1-.113))
#ATE=-.113, N=85, 95% CI is -.1803 to -.0457


##GAIN AND LOSS##


#Environmentalism
quantile(NEP, na.rm=T) #25%=2.6, 75%=3.8
enviro_df <- subset(kuni_df, NEP>=3.8)
nonenviro_df <- subset(kuni_df, NEP<=2.6)

attach(enviro_df)
enviro_df$treat_enviro[ecogain==1] <- "ecogain"
enviro_df$treat_enviro[ecoloss==1] <- "ecoloss"
enviro_df$treat_enviro[econgain==1] <- "econgain"
enviro_df$treat_enviro[econloss==1] <- "econloss"
enviro_df$treat_enviro[control==1] <- "control"
attach(enviro_df)
support_enviro <- as.numeric(project_support==1)
summary(project_support)
summary(logit_enviro <- glm(support_enviro ~ as.factor(treat_enviro), data=enviro_df, family=binomial(link="logit"))) 
#eco-loss positive, sig
#eco-gain positive but marginal
#econ are both negative but non-sig

#FOR GAIN
mean(support_enviro[treat_enviro=="ecogain" | treat_enviro=="econgain"]) - mean(support_enviro[treat_enviro=="control"])
length(support_enviro[treat_enviro=="ecogain" | treat_enviro=="econgain"])
.045 + c(-qnorm(0.975),qnorm(0.975))*sqrt((1/136)*.045*(1-.045))
#ATE=.045, N=136, 95% CI is .010 - .080

mean(support_nonenviro[treat_nonenviro=="ecogain" | treat_reps=="econgain"], na.rm=T) - mean(support_nonenviro[treat_nonenviro=="control"], na.rm=T)
length(support_nonenviro[treat_nonenviro=="ecogain" | treat_nonenviro=="econgain"])
.19627 + c(-qnorm(0.975),qnorm(0.975))*sqrt((1/124)*.19627*(1-.19627))
#ATE=.196, N=124, 95% CI is .126 - .266

#FOR LOSS
mean(support_enviro[treat_enviro=="ecoloss" | treat_enviro=="econloss"]) - mean(support_enviro[treat_enviro=="control"])
length(support_enviro[treat_enviro=="ecoloss" | treat_enviro=="econloss"])
.115 + c(-qnorm(0.975),qnorm(0.975))*sqrt((1/134)*.115*(1-.115))
#ATE=.115, N=134, 95% CI is .061 - .169

mean(support_nonenviro[treat_nonenviro=="econloss" | treat_reps=="ecoloss"], na.rm=T) - mean(support_nonenviro[treat_nonenviro=="control"], na.rm=T)
length(support_nonenviro[treat_nonenviro=="econloss" | treat_nonenviro=="ecoloss"])
.2502 + c(-qnorm(0.975),qnorm(0.975))*sqrt((1/115)*.2502*(1-.2502))
#ATE=.250, N=115, 95% CI is .171 - .329


mean(support_inds[treat_inds=="econgain" | treat_inds=="econloss"])
mean(support_inds[treat_inds=="control"])
length(support_inds[treat_inds=="econgain" | treat_inds=="econloss"])
.113 + c(-qnorm(0.975),qnorm(0.975))*sqrt((1/85)*(.113)*(1-.113))
#ATE=-.113, N=85, 95% CI is -.1803 to -.0457


