---
title: "Kuni Invasive Species Data Analysis"
author: "Elizabeth Hiroyasu"
date: "May 23, 2017"
output:
  pdf_document: default
  html_document: default
---
##Abstract 
Alex DeGolia
Environmental managers face major challenges related to not only how to implement projects, but also how to communicate their value to the public. Effective communication can mitigate public opposition while increasing public and political support for environmental management. In this study, we evaluate how to communicate the benefits of environmental management in ways that achieve these goals. To do so, we field a framing experiment that utilizes a two (economic, ecological) by two (gain, loss) factorial design to evaluate how the public responds to messages highlighting different potential benefits of an invasive species management project. We find that ecological messages lead to significantly more support for invasive species management than economic frames and that loss frames are more effective than gain frames. We also find that treatment responses differ across a number of covariates including political party identification and environmental concern. Results suggest that the public is more concerned with intrinsic environmental value than economic value and that people are more concerned with preventing further environmental degradation than helping promote environmental health.
```{r setup, echo=FALSE}
 library(devtools)
 library(roxygen2)
 load_all("./GainLossPackage")
 library(GainLossPackage)
```


###Variable Analysis
```{r echo=FALSE, warning=FALSE, message=FALSE}
source("KuniSource.R")
```
###Primary Analysis Using:
1. Project Support (binary)
2. Strength of Support from 1 (strongly oppose) to 6 (strongly support)
3. Write letter to CDFW (still need to figure out coding for this)

##binary support
```{r}
support_binary <- as.numeric(project_support==1)
kuni.treat.df$support_binary <- support_binary
summary(as.factor(support_binary)) #786 support, 291 oppose; 72.98% of people support
```


##Independent Variables
Primary Analysis Using the Following:
Demographic variables: race, gender, age (continuous), age (squared, for non-linear effects), rural/urban, occupation
Resource variables: education, HH income
Political variables: party ID, ideology
Environmental variables: NEP, animal rights

#TREATMENTS
Categorical Variable for Treatment
```{r warning=FALSE, message=FALSE}
kuni.treat.df<-df.treat(kuni_df)
summary(as.factor(kuni.treat.df$treat))
```

#Pooled
```{r warning=FALSE, message=FALSE}
summary(as.factor(kuni.treat.df$ecoecon)) 
summary(as.factor(kuni.treat.df$gainloss))

#reference level
treat_factor <- as.factor(kuni.treat.df$treat)
kuni.treat.df<- within(kuni.treat.df, treat<- relevel(treat_factor, ref = "control"))
```

##Strength of support/opposition
```{r}

kuni.treat.df$support_oppose[support_strength==1] <- 6
kuni.treat.df$support_oppose[support_strength==2] <- 5
kuni.treat.df$support_oppose[support_strength==3] <- 4
kuni.treat.df$support_oppose[oppose_strength==1] <- 3
kuni.treat.df$support_oppose[oppose_strength==2] <- 2
kuni.treat.df$support_oppose[oppose_strength==3] <- 1

summary(kuni.treat.df$support_oppose) #mean=4.16
summary(as.factor(kuni.treat.df$support_oppose)) #Breakdown: 1=118, 2=128, 3=45, 4=173, 5=399, 6=213
hist(kuni.treat.df$support_oppose) #skew toward positive end. could transform.
support_oppose2 <- kuni.treat.df$support_oppose**2 #transform for normality
hist(support_oppose2)
summary(as.factor(support_strength))

#for just support
kuni_df$support_strength2[support_strength==1] <- 3
kuni_df$support_strength2[support_strength==2] <- 2
kuni_df$support_strength2[support_strength==3] <- 1
head(kuni_df)
```



##Demographic Variables
#Race
469 non-white or latino, 601 non-latino white. This translates to 56.2% white, 20.1% hispanic/latino, 17.3% asian, 5.9% black, 3.7% american indian, 2% pacific islander (combined 43.8% non-white or latino).

CA population: 38% non-hispanic white, 39% hispanic, 13% asian, 6% black, <1% each pacific islander & american indian, 3% mixed race

US population: 76% white (incl hispanic), 17% hispanic (any race), 14% black, 6% asian, 2% american indian, <1% pacific islander
```{r warning=FALSE, message=FALSE}
attach(kuni.treat.df)

white[is.na(white)] <- 0
sum(white)

black[is.na(black)] <- 0
sum(black)

am_indian[is.na(am_indian)] <- 0
sum(am_indian)

asian[is.na(asian)] <- 0
sum(asian)

pac_islander[is.na(pac_islander)] <- 0
sum(pac_islander)

nonwhite <- as.numeric(black==1 | am_indian==1 | asian==1 | pac_islander==1 | latino==1)
sum(nonwhite, na.rm=TRUE)
```

#Rural vs Urban
367 urban, 450 suburban, 260 rural; 24.1% rural, 75.9% urban/suburban
```{r warning=FALSE, message=FALSE}
urban<-as.numeric(urban_rural==1)
sum(urban)

suburban<-as.numeric(urban_rural==2)
sum(suburban)

rural <- as.numeric(urban_rural==3)
sum(rural)
```

#Age
```{r warning=FALSE, message=FALSE}
summary(age) #mean=43.59, min=18, max=92
sd(na.omit(age))

#Age^2 for non-linear age effects (unlikely)
age2 <- age**2
```

#Occupation
```{r warning=FALSE, message=FALSE}
summary(as.factor(occupation))
summary(as.factor(employment_status)) 
employed <- as.numeric(employment_status==1 | employment_status==2)
unemployed <- as.numeric(employment_status==3 | employment_status==4)
```

#Gender
```{r warning=FALSE, message=FALSE}
male <- as.numeric(gender==1)
summary(as.factor(male)) #687 females, 390 males; 63.8% women
```

##Resource Variables
#Education
```{r warning=FALSE, message=FALSE}
summary(as.factor(highest_degree)) #only 10 people not HS grads
college_degree <- as.numeric(highest_degree>=5)
summary(as.factor(college_degree)) #585 people no college degree, 491 BA or higher
```

#Income
```{r warning=FALSE, message=FALSE}
summary(as.factor(hhincome))
length(hhincome)

```

#Values
```{r, echo=FALSE, warning=FALSE, message=FALSE}
calc_values<-function(df, v1, v2, v3){
  dat<-rowSums(df[,c(v1, v2, v3)], na.rm=TRUE)
}

altruism<-calc_values(kuni.treat.df, v1="male_altruism1", v2="male_altruism2", v3="male_altruism3")
egoism<-calc_values(kuni.treat.df, v1="male_ego1", v2="male_ego2", v3="male_ego3")
biospherism<-calc_values(kuni.treat.df, v1="male_bio1", v2="male_bio2", v3="male_bio3")
male_values<-data.frame(altruism, egoism, biospherism)

altruism<-calc_values(kuni.treat.df, v1="female_altruism1", v2="female_altruism2", v3="female_altruism3")
egoism<-calc_values(kuni.treat.df, v1="female_ego1", v2="female_ego2", v3="female_ego3")
biospherism<-calc_values(kuni.treat.df, v1="female_bio1", v2="female_bio2", v3="female_bio3")
female_values<-data.frame(altruism, egoism, biospherism)

values_tot<-female_values+male_values
values_adj<-values_tot/3

kuni.treat.df<-cbind(kuni.treat.df, values_adj)
#write.csv(kuni.treat.df, "Kuni_Data_11_14_IncValues.csv")
```

###Altruistic Values
```{r, echo=FALSE}
summary(values_adj$altruism)
```

###Egoistic Values
```{r, echo=FALSE}
summary(values_adj$egoism)
```

###Biospheric Values
```{r, echo=FALSE}
summary(values_adj$biospherism)
```


#Political Variables
##Party ID
```{r warning=FALSE, message=FALSE}
#specify independent as reference level
kuni.treat.df <- within(kuni.treat.df, partyid <- relevel(as.factor(partyid), ref=3))
republican <- as.numeric(partyid==1)
sum(republican)#302 republicans, 28%

democrat <- as.numeric(partyid==2) 
sum(democrat)#515 dems, 47.8%

independent <- as.numeric(partyid==3 | partyid==4) #260 independent/other, 24.1%
sum(independent)
```

#Ideology
```{r, echo=FALSE, warning=FALSE, message=FALSE}
summary(ideology) #mean=3.68, min=1, max=7; #64 NAs ("Haven't thought about this much")
quantile(ideology, na.rm=T) #25%=2, 75%=5
sd(na.omit(ideology))
#moving toward "conservative"
```

#Voting Behavior
```{r, echo=FALSE, warning=FALSE, message=FALSE}
trump_dummy <- as.numeric(votechoice==1)
clinton_dummy <- as.numeric(votechoice==2)
voted <- as.numeric(vote2016==4)
sum(voted, na.rm=TRUE)
```

#Immigration
```{r, echo=FALSE, warning=FALSE, message=FALSE}
immigration_decrease <- as.numeric(immigration_change==3)
sum(immigration_decrease, na.rm = TRUE)
```

##Environmental Variables#
#New Ecological Paradigm
```{r, echo=FALSE, warning=FALSE, message=FALSE}
NEP <- (as.numeric(nep1) + (6-as.numeric(nep2_rev)) + (6-as.numeric(nep3_rev))
        + as.numeric(nep4) + as.numeric(nep5))/5
summary(NEP) #mean=3.30, median=3.2; 25%=2.6, 75%=3.8
hist(NEP) #pretty close to normally distributed
sd(na.omit(NEP))
nep2 <- 6-nep2_rev
nep3 <- 6-nep3_rev
NEP_table <- cbind(nep1, nep2, nep3, nep4, nep5)
alpha(NEP_table) #alpha=.64, not great. about as good as it can be, though.
```

#Animal Rights
```{r, echo=FALSE, warning=FALSE, message=FALSE}
animalrights <- (as.numeric(animals_suffering) + as.numeric(animals_displace) + as.numeric(animals_veg) + (6-as.numeric(animals_humanuse_rev)))/4
summary(animals_suffering) #mean=4.07, median=4.0; 25%=4, 75%=5; min=1, max=5

human_rev <- 6-animals_humanuse_rev
animals_table <- cbind(animals_suffering, animals_displace, animals_veg, human_rev)
alpha(animals_table) #alpha=.61, pretty poor internal reliability when all four included
sd(animalrights, na.rm=T)
```

```{r, echo=FALSE}
#Saving the kuni.treat.df for later use
write.csv(kuni.treat.df, file="Kuni_treat_df.csv")
```

