---
title: "PartyID"
author: "Elizabeth Hiroyasu"
date: "June 27, 2017"
output:
  pdf_document: default
  html_document: default
---
This analysis examines the role of party identity in determining support for invasive species management.

```{r setup, echo=FALSE}
 library(devtools)
 library(roxygen2)
 load_all("GainLossPackage")
 library(GainLossPackage)
 
 source("KuniSource.R")
 kuni.treat.df<-read.csv("./data/Processed/Kuni_treat_df.csv", header=TRUE)
```

#Categorical and Pooled data on Treatments
```{r warning=FALSE, message=FALSE}
summary(as.factor(kuni.treat.df$treat))
summary(as.factor(kuni.treat.df$ecoecon)) 
summary(as.factor(kuni.treat.df$gainloss))

#reference level
treat_factor <- as.factor(kuni.treat.df$treat)
kuni.treat.df<- within(kuni.treat.df, treat<- relevel(treat_factor, ref = "control"))
```

##Subsetting the data by party
```{r}
reps_df <- subset(kuni.treat.df, partyid==1)
summary(reps_df$treat)

dems_df <- subset(kuni.treat.df, partyid==2)
summary(dems_df$treat)

inds_df <- subset(kuni.treat.df, partyid==3)
summary(inds_df$treat)
```

##Republican Support
```{r, echo=FALSE, warnings=FALSE, message=FALSE}
rep_summary<-treatment_effect(reps_df)
summary(rep_support<-rep_summary$support_vec)#This is different from what alex found (0.764)
summary(rep_summary$ecogain)#Alex= #0.793
summary(rep_summary$ecoloss)# Alex= 0.833
summary(rep_summary$econgain)#Alex=0.732
summary(rep_summary$econloss)#Alex=0.793
summary(rep_summary$control)#Alex=0.660
#Ordering: eco-loss, econ-loss & eco-gain (tied), econ-gain, control

rep_chi<-chisq.test(rep_support, reps_df$treat) #not significant
rep_chi
p.adjust(rep_chi$p.value, method="bonferroni", n=3)

rep_summary_df<-rep_summary$te.df
rep_summary_df$party<-rep("reps", dim(rep_summary_df)[1])

summary(logit_reps <- glm(project_support==1 ~ as.factor(reps_df$treat), data=reps_df, family=binomial(link="logit")))
```

##Democratic Support
```{r, echo=FALSE, warning=FALSE, message=FALSE}
dem_summary<-treatment_effect(dems_df)
summary(dem_support<-dem_summary$support_vec) #0.697 is overall number
summary(dem_summary$ecogain) #Alex=0.733
summary(dem_summary$ecoloss)#Alex=0.885
summary(dem_summary$econgain)#Alex=0.643
summary(dem_summary$econloss)#Alex=0.702
summary(dem_summary$control)#Alex=0.558
#Ordering: eco-loss, eco-gain, econ-loss, econ-gain, control

dem_chi<-chisq.test(dem_support, dems_df$treat)
dem_chi
p.adjust(dem_chi$p.value, method="bonferroni", n=3)

dem_summary_df<-dem_summary$te.df
dem_summary_df$party<-rep("dem", dim(dem_summary_df)[1])

summary(logit_dems <- glm(project_support==1 ~ as.factor(treat), data=dems_df, family=binomial(link="logit"))) 
```

##Independent Support
```{r echo=FALSE}
ind_summary<-treatment_effect(inds_df)
summary(ind_support<-ind_summary$support_vec)#0.746 is overall number
summary(ind_summary$ecogain)#Alex=0.818
summary(ind_summary$ecoloss)#Alex=0.837
summary(ind_summary$econgain)#Alex=0.600
summary(ind_summary$econloss)#Alex=0.720
summary(ind_summary$control)#Alex=0.714
#Ordering: eco-loss, eco-gain, econ-loss, control, econ-gain

ind_chi<-chisq.test(ind_support, inds_df$treat)
ind_chi
p.adjust(ind_chi$p.value, method="bonferroni", n=3)

ind_summary_df<-ind_summary$te.df
ind_summary_df$party<-rep("ind", dim(ind_summary_df)[1])

summary(logit_inds <- glm(project_support==1 ~ as.factor(treat), data=inds_df, family=binomial(link="logit"))) 
```

##Plotting al parties together
```{r echo=FALSE}
theme_update(plot.title = element_text(hjust = 0.5))
party.df<-rbind.data.frame(rep_summary_df, dem_summary_df, ind_summary_df)

ggplot(party.df, aes(x=treat_cat, y=ATE, fill=party)) + 
  geom_bar(position=position_dodge(), stat="identity") +
  geom_errorbar(aes(ymin=ATE-se, ymax=ATE+se),
                width=.2, position=position_dodge(.9)) +
  xlab("Treatment Category") + ylab("Average Treatment Effect")+
  #scale_fill_hue(name="Party", labels=c("Dem", "Ind", "Rep")) +
  ggtitle("Treatment Effect by Party ID")

#using boxplot instead
ggplot(party.df, aes(x=party, y=ATE, fill=treat_cat)) +
  geom_boxplot() +
  geom_errorbar(aes(ymin=ATE-se, ymax=ATE+se),
                width=.2, position=position_dodge(.9)) + ggtitle("Framing Effects by Party ID") +
  xlab("Party ID") + ylab("Average Treatment Effect") +
  #scale_x_discrete(labels=c("Rep", "Dem", "Ind")) +
  facet_grid(.~treat_cat)

```
Potential major heterogeneous treatment effects: eco-loss for dems, eco-gain for reps, both econ for reps.
Republicans seem much more responsive to gain frames, dems somewhat more responsive to loss frames. Dems also much less responsive to control frame as compared to republicans. Independents seems somewhere in between.

##Pooled Ecological Treatments
*note that the support_func that generates these results uses the following calculation to generate the ci:
 ci<-ATE + c(-qnorm(0.975),qnorm(0.975))*sqrt(abs((1/N)*ATE*(1-ATE)))
```{r}
rep_ecosupport<-support_func(rep_support, treat.type=c("ecogain", "ecoloss", "control"), reps_df)
rep_ecosupport

dem_ecosupport<-support_func(dem_support, treat.type=c("ecogain", "ecoloss", "control"), dems_df)
dem_ecosupport

ind_ecosupport<-support_func(ind_support, treat.type=c("ecogain", "ecoloss", "control"), inds_df)
ind_ecosupport
```



##Pooled Economic treatments
```{r}
rep_econsupport<-support_func(rep_support, treat.type=c("econgain", "econloss", "control"), reps_df)
rep_econsupport

dem_econsupport<-support_func(dem_support, treat.type=c("econgain", "econloss", "control"), dems_df)
dem_econsupport

ind_econsupport<-support_func(ind_support, treat.type=c("econgain", "econloss", "control"), inds_df)
ind_econsupport
```



##Pooled Gain Treatments
```{r}
rep_gainsupport<-support_func(rep_support, treat.type=c("ecogain", "econgain", "control"), reps_df)
#Alex: ATE=.075, N=120, 95% CI is .028 - .122
rep_gainsupport

dem_gainsupport<-support_func(dem_support, treat.type=c("ecogain", "econgain", "control"), dems_df)
#Alex: ATE=.142, N=208, 95% CI is .094 - .189
dem_gainsupport

inds_gainsupport<-support_func(ind_support, treat.type=c("ecogain", "econgain", "control"), inds_df)
#Alex: ATE=-.043, N=93, 95% CI is -.084 to -.002
inds_gainsupport
```



##Pooled Loss Treatments
```{r}
rep_loss<-support_func(rep_support, treat.type=c("ecoloss", "econloss", "control"), reps_df)
#Alex: ATE=.137, N=122, 95% CI is .076 - .198
rep_loss

dem_loss<-support_func(dem_support, treat.type=c("ecoloss", "econloss", "control"), dems_df)
#Alex: ATE=.243, N=199, 95% CI is .184 - .303
dem_loss

ind_loss<-support_func(ind_support, treat.type=c("ecoloss", "econloss", "control"), inds_df)
#Alex: ATE=-.024, N=92, 95% CI is -.055 to -.007
ind_loss
```


